---
title: "London Marathon Shiny App"
author: "Campbell Easton"
date: "2 March 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is a presentation for Project 3 of the Developing data products coursera course by John Hopkins University.

The aim of this project is to produce an interactive shiny app which can be deployed the shiny.io website. You can see the app on shiny.io here: https://eastc5.shinyapps.io/London_Marathon_Shiny_App/
And the associated source code on github here: https://github.com/eastc5/London_Marathon_Shiny_App/


##App Description 
My app uses data from the 2016 London marathon to visualize finishing times as a histogram and  calculates quantiles for expected finishing times so that prospective London Marathon runners can see where their goal times will place them in the field for all runners and in their respective age and sex category. 

On the next page is a screen shot of the app, but go see the real thing here:
https://eastc5.shinyapps.io/London_Marathon_Shiny_App/   

## App image

```{r,echo=FALSE}
library(png)
library(grid)
img <- readPNG("Capture.PNG")
 grid.raster(img)
```

## Plotly Teaser

Below is a interactive histogram of 2016 London marathon finishing times built using ```plotly``` which the shiny app is based on.

```{r, echo=FALSE ,warning=FALSE,message=FALSE} 

library(plotly)
#load data
Rdata<-read.csv("./data/VLM2016.csv")

Running1<-Rdata
#convert finish time from charater to datetime format
Running1$FINISH<-strptime(Rdata$FINISH,format = "%H:%M:%S",tz="GMT")

#creat the ggplot histogram
p <- ggplot(Running1, aes(x=FINISH, fill = Gender))
p <- p + geom_histogram(binwidth=300,position = "dodge") 
p <- p + scale_x_datetime(date_labels = "%H:%M:%S", date_breaks = "1 hour")

#extract the plotly build so the tool tip text can be adjusted to remove date from the time
g <- plotly_build(p)

#for men[[1]] and women[[2]]
for (i in 1:2) { 
    
    #extract txt and replace date time with time HH:MM:SS fomat
b<- g$x$data[[i]]$x %>% as.POSIXlt(origin = "1970-01-01") %>% format("%H:%M:%S") 

#re-create the text string
v<-paste("Count: ",g$x$data[[i]]$y, "<br>","Finish: ",
         b,"<br>", "Gender: ",g$x$data[[i]]$name)

#sub it back in to the plotly build list
g$x$data[[i]]$text<-v

}

ggplotly(g)
```